Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model

### 2020-08-06 paper/paper.tex
20200806 13:50

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) (a) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase. The three FM phases different from each other in the direction of the ordered moment, and also the four stripe phases are distinguished by their moment directions, see main text for details. (b) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=1.5\pi$. (c) The red (blue) line is $-\partial^2E_0/\partial\alpha^2$ ($E_0$) versus $\alpha$ with $\beta=0$. (d) The red (blue) line is $-\partial^2E_0/\partial\beta^2$ ($E_0$) versus $\beta$ with $\alpha=0.3\pi$.}
\end{figure*}

The quantum phase diagrams obtained by the exact-diagonalization method for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:QuantumPhaseDiagram}(a). The phase boundaries are obtained from the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.

@@

Our classical Monte Carlo simulation found FM ordered states with the right moment direction for majority of the area marked as FM phase (see Fig.~\ref{fig:ClassicalPhaseDiagram}) except for the pure $\Gamma$ term. For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found. When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix~\ref{apx:AppendixA} for details). Based on these observation, it is reasonable to say that the GS of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions. For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM ordered state as the GS. On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS.

In light of the classical analysis, we conjecture the main differences between these FM phases lies in the ordered moment direction. To further confirm our hypothesis, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435} to extract the moment direction of these FM phases from our ED cluster ground state. Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (such as FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. The resulting probability maps for representive model parameters of FM-A and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(c) and (d). It is worth to note that the large overlap between the exact cluster GS and FM ordered cluster spin-coherent state again provides solid evidence that the corresponding areas are FM phases. For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction). In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis. However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction. For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(c)) with all directions degenerate. The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(d)). The ground states of the quantum model in these areas are similar to their classical analogue except for the pure $\Gamma$ model. For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order. However, for the quantum model, quantum flucations select the FM ordered states lie in the lattice plane as GS out of an otherwise infinitely degenerate manifold of classical states. Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM state perpendicular to the lattice plane is selected as the GS. This selection of states among degenerate classical ground states is the so called \emph{order-from-disorder} mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.

@@

Inspired by the previous discussion of those FM phases, we perform the same analysis for these stripe phases. For stripe order, there are three degenerated spin configurations in real-space, designated as \emph{config-x}, \emph{config-y} and \emph{config-z} respectively. For \emph{configx}, the spins on the chains along the $x$-bond direction form ferromagnetic chains and adjacent chains are anti-parallel. Similarly, the ferromagnetic chains along the $y$-bond and $z$-bond direction for \emph{config-y} and \emph{config-z} respectively. For \emph{config-x}, the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} per lattice site is
\begin{eqnarray}
    E_{StripeX}^{c} & = & -(J + K) + 2 K v^x v^x \nonumber \\
        & & +\: 2 \Gamma (v^y v^z - v^z v^x - v^x v^y)
        \label{eq:EcStripeX}
\end{eqnarray}
and the energy for \emph{config-y} and \emph{config-z} can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$. The ordered moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$. In general ($K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has six extreme points where the first derivatives with respect to $v_x$, $v_y$ and $v_z$ equal zero. Here we give three of them explicitly and the other three are opposite to the given ones
\begin{subequations}
    \label{eq:whole}
    \begin{eqnarray}
        & \bm{v}_0:& \quad v_{0}^{y}=-v_{0}^{z} = 1/\sqrt{2}, \quad v_{0}^{x} = 0 \label{eq:v0} \\
        & \bm{v}_1:& \quad v_{1}^{y}=v_{1}^{z} = f_{1}(K, \Gamma), \quad v_{1}^{x} = g_{1}(K, \Gamma) v_{1}^{y} \label{eq:v1} \\
        & \bm{v}_2:& \quad v_{2}^{y}=v_{2}^{z} = f_{2}(K, \Gamma), \quad v_{2}^{x} = g_{2}(K, \Gamma) v_{2}^{y} \label{eq:v2}
    \end{eqnarray}
\end{subequations}
see Appendix~\ref{apx:AppendixB} for their explicit expressions.

For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $v^x = 0$ which means that \emph{config-x} prefers to lie in the $yz$ plane. An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\bm{v}_0$ direction whereas negative $\Gamma$ drives it to the $\bm{v}_1$ direction. When $\Gamma=0, K<0$, the ordered moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\bm{v}_1$ direction. All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation. However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$ (see Appendix~\ref{apx:AppendixA} for details). The GS of the classical HK model near the antiferromagetic Kitaev point ($K=1$) is high degenerate and both positive and negative $\Gamma$ interactions select specific stripe ordered state as the GS.

To determined the ordered moment direction of those stripe phases in the quantum phase diagram, we construct stripe ordered cluster spin-coherent states and calculate their probabilities in the ED ground state. For brevity, we only construct cluster spin-coherent state based on \emph{config-x} and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(a), (e), (f), (b) for Stripe-A, Stripe-B, Stripe-C, Stripe-D respectively. The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction. The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for \emph{config-x} from classical considerations, our ED results show that this situation also applies at quantum limit. On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(b) indicates that the ordered moment pointing to the $y$ and $z$-axis direction. The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for \emph{config-x}, $\pm x$, $\pm z$ for \emph{config-y}, $\pm x$, $\pm y$ for \emph{config-z}), more importantly it is a signature of large quantum flucations in the GS. It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states. Stripe-D different from Stripe-A in the direction of the ordered moment direction. To be specific, for a certain spin configuration, the ordered moment would along only one of the $x, y, z$-axis direction in the Stripe-A phase and point to the other two axes directions for the Stripe-D phase. When $\alpha=0.7\pi,\beta=0.66\pi$, the probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, whereas $P(\theta, \phi)$ is clearly peaked at the direction given by Eq.~\eqref{eq:v0} for $\alpha=0.3\pi, \beta=0.25\pi$ (See the green solid circle in \ref{fig:Proabilities}(e) and (f)). Considering the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the exact cluster GS, it is reasonable to say that the stripe ordered ground states for the classical $J-K-\Gamma$ model in these areas persist in the quantum limit and the ordered moments of the quantum states coincide with their classical analogue. The reduced probabilities $P_{max} < \frac{1}{6}$ may be attributed to quantum flucations.

In the HK limit, there exist a stripe phase (i.e., Stripe-A) when $J>0, K<0$ and the ordered moment along the $x,y,z$-axis direction. When an infinitesimal $\Gamma$ interaction is included, both positive and negative couplings tilting the ordered moment orientation away from the cubic axes directions, yielding the Stripe-B phase. The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:AppendixB} for details). As for the Stripe-D phase near the AF Kitaev point, the effect of the $\Gamma$ term is again tilting the ordered moment away from the cubic axes directions though the effects for positive and negative couplings are different. An infinitesimal positive $\Gamma$ interaction changes the ordered moment orientation from the cubic axes directions to the direction specified by Eq.~\eqref{eq:v0} and its equivalents (see Appendix~\ref{apx:AppendixB} for details). On the other hand, when an infinitesimal negative $\Gamma$ interaction is introduced, the ordered moment is rotated to the direction determined by Eq.~\eqref{eq:v1} and its equivalents.

@@

Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:QuantumPhaseDiagram}. For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ. Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase. To have further understanding of the characteristics of this phase, we also calculate the spin excitation spectrum and a typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}(b). The high intensities at both the center and M-points of the first BZ is consistent with the SMSF data. Moreover, there are continuum spectrum at high energy which is a characteristic of QSL. However, the $A(\mathbf{k}, \omega)$ does not have intensities at $\omega = 0$ which indicates the system described by the corresponding model Hamiltonian is gapped. Combined with all of the above results, we propose the GS of quantum $J-K-\Gamma$ model at the green area is a gapped QSL.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/Spectrum.pdf}
    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.10\pi$. $A(\bm{k}, \omega)$ is draw along the path $M-\Gamma-M-\Gamma$.}
\end{figure}

@@

\section{\label{apx:AppendixA}Phase Boundaries in the Quantum Phase Diagram}

@@

\section{\label{apx:AppendixB}Quantum Static Spin Structure Factors}

@@

\section{\label{apx:AppendixC}Classical ground states for some special model parameters}

@@

\section{\label{apx:AppendixD}Classical energy and moment direction of the stripe ordered states}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total nine phases including three different FM phases denoted as FM-A, FM-B and FM-C, three different stripe phases designated as Stripe-A, Stripe-B and Stripe-C, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase. The three FM phases different from each other in the direction of the ordered moment, and also the three stripe phases are distinguished by their moment directions, see main text for details.}
\end{figure*}

The quantum phase diagrams obtained by the exact-diagonalization method for $\Gamma \geq 0$ and $\Gamma \leq 0$ are presented in Fig.~\ref{fig:QuantumPhaseDiagram}. The phase boundaries are obtained from the location of singularities in $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$.

@@

Our classical Monte Carlo simulation found FM ordered states with the right moment direction for majority of the area marked as FM phase (see Fig.~\ref{fig:ClassicalPhaseDiagram}) except for the pure $\Gamma$ term. For pure positive $\Gamma$ interaction, apart from the FM order lie in the lattice plane, we also found disordered states which have the same energy as the FM state but no states with lower energy were found. When $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state appear (see Appendix~\ref{apx:DegeneratedStates} for details). Based on these observation, it is reasonable to say that the GS of the classical $\Gamma$ model is highly degenerate though the degeneracy may be lifted by introducing other interactions. For example, a ferromagnetic ($J<0$) Heisenberg interaction would break the degeneracy and select the FM ordered state as the GS. On the other hand, when positive Heisenberg interaction is included, which introduces further frustation to the system, the FM order is unlikely to be the GS.

In light of the classical analysis, we conjecture the main differences between these FM phases lies in the ordered moment direction. To further confirm our hypothesis, we employ the method developed by Ji\v{r}\'{i} Chaloupka \emph{et  al} \cite{PhysRevB.94.064435} to extract the moment direction of these FM phases from our ED cluster ground state. Since the cluster spin-coherent state is captured only by a single pair of $(\theta, \phi)$ for collinear states (such as FM and stripe), it is easy to determine the direction of the ordered moment by inspecting the probability map $P(\theta, \phi) = | \langle \Psi (\theta, \phi) | GS \rangle |^2$. The resulting probability maps for representive model parameters of FM-A and FM-C phases are shown in Fig.~\ref{fig:Proabilities}(a) and (b). It is worth to note that the large overlap between the exact cluster GS and FM ordered cluster spin-coherent state again provides solid evidence that the corresponding areas are FM phases. For pure Heisenberg model, the FM state is spin rotational invariant and the ordered moment can point any direction. The easy axis Kitaev interaction breaks the accidental spin rotational symmetry, pinning the orderings to the axis direction (i.e., $x$, $y$, $z$ direction). In other words, the ordered moment of the FM-B phase is in the direction of the $x,y,z$-axis. However, when the off-diagonal $\Gamma$ term is introduced, which would compete with Kitaev interaction, the moment orientation will deviate from the axis direction. For the FM-A phase, the probability map reveals the moment being constrained to the lattice plane (marked by the green dashed line in Fig.~\ref{fig:Proabilities}(a)) with all directions degenerate. The probability map for the FM-C phase is clearly peaked at the direction perpendicular to the lattice plane (marked by the green solid circle in \ref{fig:Proabilities}(b)). The ground states of the quantum model in these areas are similar to their classical analogue except for the pure $\Gamma$ model. For $\Gamma=1$, the GS of the classical model is highly degenerate including FM ordered states and states with no long range order. However, for the quantum model, quantum flucations select the FM ordered states lie in the lattice plane as GS out of an otherwise infinitely degenerate manifold of classical states. Similarly, the degeneracy for the classical model at $\Gamma=-1$ is lifted by quantum flucations and the FM state perpendicular to the lattice plane is selected as the GS. This selection of states among degenerate classical ground states is the so called \emph{order-from-disorder} mechanism previously emphasized by Villain and Henley in the context of the square lattice XY model \cite{PhysRevLett.62.2056} and by Oguchi \emph{et al.,} in the case of fcc antiferromagnet \cite{JPSJ.54.4494}.

@@

Inspired by the previous discussion of those FM phases, we perform the same analysis for these stripe phases. For stripe order, there are three degenerated spin configurations in real-space, designated as \emph{config-x}, \emph{config-y} and \emph{config-z} respectively. For \emph{configx}, the spins on the chains along the $x$-bond direction form ferromagnetic chains and adjacent chains are anti-parallel. Similarly, the ferromagnetic chains along the $y$-bond and $z$-bond direction for \emph{config-y} and \emph{config-z} respectively. For \emph{config-x}, the energy of the model Hamiltonian~\eqref{eq:Hamiltonian} per lattice site is
\begin{eqnarray}
    E_{StripeX}^{c} & = & -(J + K) + 2 K v^x v^x \nonumber \\
        & & +\: 2 \Gamma (v^y v^z - v^z v^x - v^x v^y)
        \label{eq:EcStripeX}
\end{eqnarray}
and the energy for \emph{config-y} and \emph{config-z} can be obtained by a cyclic permutation $x \rightarrow y \rightarrow z \rightarrow x$. The ordered moment direction of the classical stripe order is determined by the anisotropy parameters $K$ and $\Gamma$. In general ($K,\Gamma \neq 0$), $E_{StripeX}^{c}$ has six extreme points where the first derivatives with respect to $v_x$, $v_y$ and $v_z$ equal zero. Here we give three of them explicitly and the other three are opposite to the given ones
\begin{subequations}
    \label{eq:whole}
    \begin{eqnarray}
        & \bm{v}_0:& \quad v_{0}^{y}=-v_{0}^{z} = 1/\sqrt{2}, \quad v_{0}^{x} = 0 \label{eq:v0} \\
        & \bm{v}_1:& \quad v_{1}^{y}=v_{1}^{z} = f_{1}(K, \Gamma), \quad v_{1}^{x} = g_{1}(K, \Gamma) v_{1}^{y} \label{eq:v1} \\
        & \bm{v}_2:& \quad v_{2}^{y}=v_{2}^{z} = f_{2}(K, \Gamma), \quad v_{2}^{x} = g_{2}(K, \Gamma) v_{2}^{y} \label{eq:v2}
    \end{eqnarray}
\end{subequations}
see Appendix~\ref{apx:StripeMomentDirection} for their explicit expressions.

For $\Gamma=0, K>0$, it can be clearly seen from Eq.~\eqref{eq:EcStripeX} that $E_{StripeX}^{c}$ takes minimum value at $v^x = 0$ which means that \emph{config-x} prefers to lie in the $yz$ plane. An infinitesimal positive $\Gamma$ would fix the ordered moment to the $\bm{v}_0$ direction whereas negative $\Gamma$ drives it to the $\bm{v}_1$ direction. When $\Gamma=0, K<0$, the ordered moment would along the $x$-axis to have lowest energy, both positive and negative $\Gamma$ make it deviate from the $x$-axis and point to the $\bm{v}_1$ direction. All these stripe orders with the specific moment direction were found in the corresponding parameter space by our Monte Carlo simulation. However, in the HK limit ($\Gamma=0$), apart from the stripe orders lie in the axis plane, nematic orders which have the same energy were also found in the range $0 \leq |J| \ll K$ (see Appendix~\ref{apx:DegeneratedStates} for details). The GS of the classical HK model near the antiferromagetic Kitaev point ($K=1$) is high degenerate and both positive and negative $\Gamma$ interactions select specific stripe ordered state as the GS.

To determined the ordered moment direction of those stripe phases in the quantum phase diagram, we construct stripe ordered cluster spin-coherent states and calculate their probabilities in the ED ground state. For brevity, we only construct cluster spin-coherent state based on \emph{config-x} and present the resulting probability maps in Fig.~\ref{fig:Proabilities}(c), (d), (e), (f) for Stripe-A, Stripe-D, Stripe-B, Stripe-C respectively. The probability map for the Stripe-A phase has high intensity at $(\pi/2, 0)$ and $(\pi/2, \pi)$ which means the ordered moment would along the $x$-axis direction. The Stripe-A phase is connected to the FM-B phase through FST and the spins are supposed to along the $x$-axis for \emph{config-x} from classical considerations, our ED results show that this situation also applies at quantum limit. On the other hand, the relative high intensity of $P(\theta, \phi)$ at $(0, 0)$ and $(\pi/2, \pm\pi/2)$ in Fig.~\ref{fig:Proabilities}(d) indicates that the ordered moment pointing to the $y$ and $z$-axis direction. The small $P_{max}$ of about 3\% can be partly attributed to the cluster GS being a superposition of three possible stripe patterns and every pattern has four ordered moment direction (i.e., $\pm y$, $\pm z$ for \emph{config-x}, $\pm x$, $\pm z$ for \emph{config-y}, $\pm x$, $\pm y$ for \emph{config-z}), more importantly it is a signature of large quantum flucations in the GS. It is worth to note that even the GS of the classical AF Kitaev model was identified to be highly degenerate involving nematic and stripe ordered states, our ED results favor the idea that quantum flucations would select stripe ordered states as GS out of an otherwise infinitely degenerate manifold of classical states. Stripe-D different from Stripe-A in the direction of the ordered moment direction. To be specific, for a certain spin configuration, the ordered moment would along only one of the $x, y, z$-axis direction in the Stripe-A phase and point to the other two axes directions for the Stripe-D phase. When $\alpha=0.7\pi,\beta=0.66\pi$, the probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, whereas $P(\theta, \phi)$ is clearly peaked at the direction given by Eq.~\eqref{eq:v0} for $\alpha=0.3\pi, \beta=0.25\pi$ (See the green solid circle in \ref{fig:Proabilities}(e) and (f)). Considering the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the exact cluster GS, it is reasonable to say that the stripe ordered ground states for the classical $J-K-\Gamma$ model in these areas persist in the quantum limit and the ordered moments of the quantum states coincide with their classical analogue. The reduced probabilities $P_{max} < \frac{1}{6}$ may be attributed to quantum flucations.

In the HK limit, there exist a stripe phase (i.e., Stripe-A) when $J>0, K<0$ and the ordered moment along the $x,y,z$-axis direction. When an infinitesimal $\Gamma$ interaction is included, both positive and negative couplings tilting the ordered moment orientation away from the cubic axes directions, yielding the Stripe-B phase. The ordered moment orientation of the Stripe-B phase is given by Eq.~\eqref{eq:v1} and its equivalents (see Appendix~\ref{apx:StripeMomentDirection} for details). As for the Stripe-D phase near the AF Kitaev point, the effect of the $\Gamma$ term is again tilting the ordered moment away from the cubic axes directions though the effects for positive and negative couplings are different. An infinitesimal positive $\Gamma$ interaction changes the ordered moment orientation from the cubic axes directions to the direction specified by Eq.~\eqref{eq:v0} and its equivalents (see Appendix~\ref{apx:StripeMomentDirection} for details). On the other hand, when an infinitesimal negative $\Gamma$ interaction is introduced, the ordered moment is rotated to the direction determined by Eq.~\eqref{eq:v1} and its equivalents.

@@

Apart from these single-$\mathbf{Q}$ phases, we also identify a multi-$\mathbf{Q}$ phase, see the green area in Fig.~\ref{fig:QuantumPhaseDiagram}. For $J$, $K$, $\Gamma$ in this area, the SMSF has high intensities at both the center and M-points of the first BZ. Fig.~\ref{fig:StructureFactors}(f) is a typical SMSF profile of this phase. To have further understanding of the characteristics of this phase, we also calculate the spin excitation spectrum and a typical $A(\mathbf{k}, \omega)$ profile is shown in Fig~\ref{fig:Spectrum}. The high intensities at both the center and M-points of the first BZ is consistent with the SMSF data. Moreover, there are continuum spectrum at high energy which is a characteristic of QSL. However, the $A(\mathbf{k}, \omega)$ does not have intensities at $\omega = 0$ which indicates the system described by the corresponding model Hamiltonian is gapped. Combined with all of the above results, we propose the GS of quantum $J-K-\Gamma$ model at the green area is a gapped QSL.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/Spectrum.pdf}
    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.10\pi$. $A(\bm{k}, \omega)$ is draw along the path $M-\Gamma-M-\Gamma$.}
\end{figure}

@@

\section{\label{apx:PhaseBoundary}Phase Boundaries in the Quantum Phase Diagram}

@@

\section{\label{apx:SSF}Quantum Static Spin Structure Factors}

@@

\section{\label{apx:DegeneratedStates}Classical ground states for some special model parameters}

@@

\section{\label{apx:StripeMomentDirection}Classical energy and moment direction of the stripe ordered states}
